Supporting Information

### 2015-08-19 ms.Rmd
rerun pipeline from DESeq2

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("svg", "cairo_pdf"),
               fig.width=3.150,
               fig.height=6.3,
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

**`r I(pasteLabel("Figure S", s_figCount, "sf_mfuzzPca"))`**: Classical multidimensional scaling of Euclidean distances between transformed read counts for clustered genes.

@@

# References

@@

>>>>

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("png", "cairo_pdf"),
               fig.width=3.150,
               fig.height=6.3,
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

**`r I(pasteLabel("Figure S", s_figCount, "sf_mfuzzPca"))`**: Classical multidimensional scaling (MDS) of Euclidean distances between transformed read counts for clustered genes.

@@

@@

# References (move to before *Tables*)

### 2015-08-19 si.Rmd
rerun pipeline from DESeq2

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: svg
  word_document:
    fig_caption: yes
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
bibliography: bib/test.bib
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("svg", "cairo_pdf"),
               fig.width=6.614,
               fig.height=6.614,
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

@@

### Fuzzy *c*-means clustering

```{r mfuzz}
print(sf_mfuzzCentroids)

print(sf_mfuzzPca)
```

>>>>

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
bibliography: bib/test.bib
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("png", "cairo_pdf"),
               fig.width=6.614,
               fig.height=6.614,
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

**`r I(pasteLabel("Table S", s_tableCount, "st_libStats"))`**: Library and sequencing statistics.

@@

**`r I(pasteLabel("Figure S", s_figCount, "sf_pca"))`**: Principal components analysis of transformed read counts for each library. The two libraries made from degraded RNA did not appear to cluster with other libraries (see `r I(pasteLabel("Table S", s_tableCount, "st_libStats"))`), suggesting that the use of degraded RNA had an effect on the quantification of read counts. For this reason these two libraries were not included in subsequent analyses.

```{r sf_mfuzzCentroids}
print(sf_mfuzzCentroids)
```

**`r I(pasteLabel("Figure S", s_figCount, "sf_mfuzzCentroids"))`**: Minimum centroid distance for 2–`r maxClust` cluster cores (*c*). Eight cluster cores were used because the rate of change of the minimum centroid distance over *c* decreases after *c* = 8.

``` {r sf_mfuzzPca}
print(sf_mfuzzPca)
```

**`r I(pasteLabel("Figure S", s_figCount, "sf_mfuzzPca"))`**: Classical multidimensional scaling (MDS) of Euclidean distances between transformed read counts for clustered genes. Genes are coloured by the cluster to which they were assigned. The separation of genes by cluster on the MDS plot supports the use of eight clusters.
